Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit summary

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the total galaxy mass \mtot{}. We adopt this ratio as a proxy for the fraction of ex-situ stars in our sample. Typical observational uncertainties are shown in the upper left hand corner. The solid grey line shows the predicted relation  derived from the Illustris simulation at $z=0$ 
          (Fig 4 in \citealt{RodriguezGomez2016}). Grey dashed lines correspond to the predicted 68 percentile of the distribution \alexie{CHECK}. \textbf{Right:} comparison between our median \mden{} profiles with the inner component of the structural decomposition of massive elliptical galaxies at $z{\sim} 0$ from \citet[][Cyan, solid]{Huang2013a}.  \alexie{A phrase about what we learn here}.  At high redshifts,  the profiles of massive galaxies  should be dominated by  the in-situ component.  We compare our profiles with the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ from \textit{HST} observations \citet[][Red, dashed]{Patel2013} and the \mden{} profile of a very massive cD galaxy at $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble Ultra-Deep Field. \alexie{Always finish with a phrase saying what we learn from this figure. Are we going to say something about redshift evolution? What is the goal?}.}
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \begin{enumerate}
        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
            significantly underestimated with shallow imaging data such as SDSS and/or 
            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser{}). 
            In contrast to previous work, our results do not depend on stacking or any 
            parametric models. 
            Moreover, the degree to which mass is underestimated depends on \mtot{}. Simple model miss more light for massive galaxies because they have more extended enveloppes. There is also a \mhalo{}-dependence of this effect and naive luminosity estimates will  miss more light for BCGs is massive halos compared to centrals in less massive halos. These effects need to be carefully taken into account when discussing topics such as the evolution of the galaxy SMF.     
        \item We show that the \mden{} profiles of massive galaxies are relatively homogenous  within 10-20 kpc. However, there is a large but continuous scatter in outer profiles of massive galaxies. Galaxies with higher \mtot{} show more prominent stellar halos and have 
            shallower outer \mden{} slopes. 
            Assuming that stellar halos are dominated by accreted stars, this result is consistent with the two-phase formation picture of massive galaxies. 
        \item We show that, on average, massive galaxies have positive ellipticity 
            gradients out to at least 60 kpc. 
            The average ellipticity profile also depend on \mtot{}: more massive 
            galaxies tend to have steeper ellipticity gradients and become more 
            elongated in the accreted stellar halo. 
            On the other hand, the average $g-r$ and $g-i$ color gradients do not 
            show clear dependence on \mtot{} within 10-60 kpc.      
    \end{enumerate}

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \textbf{Left:} Ratio of the fraction of stars between 10 to 100 kpc to the 
          total galaxy mass \mtot{}. 
          We adopt this ratio as a proxy for the fraction of ex-situ stars in our 
          sample. 
          Typical observational uncertainties are shown in the upper left hand corner. 
          The solid grey line shows the predicted relation  derived from the Illustris
          simulation at $z=0$ (Fig 4 in \citealt{RodriguezGomez2016}). 
          Regions between the grey dashed lines correspond to the range between the 
          16 and 84 percentile of the distribution. 
          \textbf{Right:} comparison between our median \mden{} profiles with the 
          inner component of the structural decomposition of massive elliptical 
          galaxies at $z<0.02$ from \citet[][Cyan, solid]{Huang2013a}.
          At higher redshifts, the \mden{} profiles of massive galaxies should be 
          dominated by the in-situ component. 
          We compare our profiles with the median \mden{} profile of massive galaxies 
          at $1.0 < z < 1.5$ from \textit{HST} observations 
          \citet[][Red, dashed]{Patel2013}. 
          Both these comparisons suggest that the \mden{} profile within 10 kpc is 
          dominated by \textit{in situ} stars, but there are already contributions
          from the accreted stars at very high \mstar{} end. 
          We also compare with the \mden{} profile of a very massive cD galaxy at
          $z{\sim} 1.1$ discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field. 
          It is likely that this object will grow into one of the very massive central
          galaxy in our sample.
          It is interesting to see that its \mden{} profile is very similar to the 
          HSC one of the most massive \mtot{} bin in the inner $\sim 20$ kpc, so the 
          following growth should mostly happen in the outskirt. 
          }
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

        \item We find that the ``total'' \mstar{} of these massive galaxies can be 
            significantly underestimated with shallow imaging data such as SDSS and/or 
            oversimplified model assumptions (e.g. the \texttt{cModel} or single-\ser{}). 
            In contrast to previous work, our results do not depend on stacking or any 
            parametric models. 
            Moreover, the degree to which stellar mass is underestimated depends on 
            \mtot{}. 
            Simple model misses more light for massive galaxies because they have 
            more extended envelopes. 
            There is also a \mhalo{}-dependence of this effect and naive luminosity
            estimates will miss more light for BCGs in more massive halos compared 
            to centrals in less massive halos.
            These effects need to be carefully taken into account when discussing 
            topics such as the evolution of the galaxy stellar mass function.

        \item We show that the \mden{} profiles of massive galaxies are relatively
            homogenous within 10-20 kpc. 
            However, there is a large but continuous scatter in outer profiles of 
            massive galaxies. 
            Galaxies with higher \mtot{} show more prominent stellar halos and have 
            shallower outer \mden{} slopes. 
            Assuming that stellar halos are dominated by accreted stars, this result 
            is consistent with the two-phase formation picture of massive galaxies.

        \item We show that, on average, massive galaxies have positive ellipticity 
            gradients out to at least 60 kpc. 
            The average ellipticity profile also depend on \mtot{}: more massive 
            galaxies tend to have steeper ellipticity gradients and become more 
            elongated in the accreted stellar halo. 
            On the other hand, the average $(g-r)$ and $(g-i)$ color gradients do 
            not show clear dependence on \mtot{} within 10-60 kpc.
